Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Add empty acknowledgments section
Remove footnote

The gold standard always evaluates $S$ at all angles, so the
correlation between it and the true angle of rotation is
undefined. The mean error of responses was $\ME{}=0.01$, indicating
that $Z$ is a sufficient approximation\footnote{The one error comes
  from a $h_0$ stimulus which is highly symmetric. Although it is
  distinct enough for the author to correctly judge when both images
  are viewed side by side, it remains to be seen whether human
  participants, viewing the images sequentially would also make the
  correct judgment.}  of $\int_R p(X_b\ \vert\ X_R)p(R)\ \mathrm{d}R$.

@@

>>>>

The gold standard always evaluates $S$ at all angles, so the
correlation between it and the true angle of rotation is
undefined. The mean error of responses was $\ME{}=0.01$, indicating
that $Z$ is a sufficient approximation of $\int_R p(X_b\ \vert\
X_R)p(R)\ \mathrm{d}R$.

@@

\textbf{Acknowledgements}

\TODO{}
